### 2014-06-06 paper/body.tex
added todo command

@@

Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}). This happens with such frequency that not only is it no longer surprising, but to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a bug somewhere in one's code. In fact, this paper's authors are now used to checking for gabor features in the first layer simply to assure ourselves that the training is at least partially working.

@@

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{\edit{Caption here...}}
\label{fig:transfer}
\end{figure}

@@

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% !TEX root = main.tex

@@

Many trained networks reported recently in the literature --- unsupervised and supervised alike --- exhibit a curious aspect in common: they all learn features that resemble gabor filters on the first layer (see Figure~\ref{fig:layer1}) \editbox{fix broken figure ref here}. This happens with such frequency that not only is it no longer surprising, but to obtain anything else on a natural-image dataset causes suspicion of poorly chosen hyperparameters or a bug somewhere in one's code. In fact, this paper's authors are now used to checking for gabor features in the first layer simply to assure ourselves that the training is at least partially working.

@@

\begin{figure}[htpb]
\begin{center}
\includegraphics[width=1\linewidth]{drawings/transfer.pdf}
\end{center}
\caption{\edit{Caption here...}}
\label{i}
\end{figure}

@@

\begin{table}[t]
\caption{Convolutional Network architecture sizes and hyperparameters. \todo{explain what R vs. S is}}
\label{tab:network_architecture}
\begin{center}
\begin{tabular}{|r|l|l|l|l|l|l|l|l|l|}
\hline
       &      & filter & number  &        &        &     &         & Maxpool        & LRN (size,        \\
name   & pad  & size   & outputs & groups & stride & R/S & Dropout & (width,stride) & $\alpha$,$\beta$) \\
\hline
conv1  &      & 11x11  & 96      & 1      & 4      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv2  & 2    & 5x5    & 256     & 2      & 1      & R   &         & 3, 2           & 5,0.0001,0.75     \\
conv3  & 1    & 3x3    & 384     & 1      & 1      & R   &         &                &                   \\
conv4  & 1    & 3x3    & 384     & 2      & 1      & R   &         &                &                   \\
conv5  & 1    & 3x3    & 256     & 2      & 1      & R   &         & 3, 2           &                   \\
fc6    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc7    &      &        & 4096    & 1      &        & R   & *       &                &                   \\
fc8    &      &        & 1000    & 1      &        & S   &         &                &                   \\
\hline
\end{tabular}
\end{center}
\end{table}
